---
title: ""
output: 
  github_document:
    pandoc_args: ["--wrap=preserve"]
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

> This repository stores the code and data used to perform the analysis presented in the manuscript *In-season predictions of daily harvest for lower Kuskokwim River subsistence salmon fisheries* by authors B. Staton, W. Bechtol, L. Coggins, and G. Decossas.

> The manuscript is under review.

[![ArticleDOI](https://img.shields.io/badge/Article-PLACEHOLDER%20IF%20ACCEPTED-blue?logo=doi&logoColor=f5f5f5)]()  
[![GitHub Repo Archive DOI](https://img.shields.io/badge/GitHub%20Repo%20Archive-PLACEHOLDER%20WHEN%20MINTED-blue?logo=github)]()

## Repository Structure

```{r subdir-table}
# define scripts and their purpose
tab = matrix(c(
  "`session-setup.R`",          "Loads packages, sets directories, creates miscellaneous objects used throughout other scripts.",
  "`make-figures.R`",           "Creates all figures in the main text",
  "`make-tables.R`",            "Creates `.csv` files containing the summarized information ready for table formatting and inclusion in main text and Supplement A.",
  "`make-residual-figures.R`",  "Creates all residual diagnostic figures in Supplement B."

), ncol = 2, byrow = TRUE)

kableExtra::kbl(tab, "markdown", col.names = c("Subdirectory", "Description"))

```

## Dependencies

### 'KuskoHarv*' Package Family

Users will need to install the R package ['KuskoHarvPred'](https://github.com/bstaton1/KuskoHarvPred).
From any R console:

```{r, eval = FALSE, echo = TRUE}
install.packages("remotes")
remotes::install_github("bstaton1/KuskoHarvPred")
```

'KuskoHarvPred' contains infrastructure to perform the key analytical tasks presented in the manuscript:

* Regression analyses (e.g., `?fit_all_subsets()`)
* Model-averaging (e.g., `?predict_model_avg()`)
* Leave-one-out analyses (`?loo_pred()`, `?loo_pred_model_avg()`, `?whole_loo_analysis()`)
* Run the [interactive web application](https://bstaton.shinyapps.io/KuskoHarvPred-tool/) (`?run_predictive_tool()`)

The analyses take some time to run, so to streamline analyses, 'KuskoHarvPred' ships with several pre-compiled output objects, which are called repeatedly throughout the scripts in this repo:

* `KuskoHarvPred:::fit_data`: contains the data set used in regression modeling
* `KuskoHarvPred:::fit_lists`: contains all fitted regression models
* `KuskoHarvPred:::loo_output`: contains leave-one-out predictions and error summaries

Three other packages (and their dependencies) will simultaneously be installed:

* ['KuskoHarvEst'](https://github.com/bstaton1/KuskoHarvEst) (`r paste0("v", packageVersion("KuskoHarvEst"))`): contains the workflow to produce harvest estimates from interview and flight data.
* ['KuskoHarvData'](https://github.com/bstaton1/KuskoHarvData) (`r paste0("v", packageVersion("KuskoHarvData"))`): contains raw interview and aerial survey data, as well as compiled harvest and effort estimates, for each drift gillnet opener monitored by the lower Kuskokwim River in-season subsistence salmon harvest monitoring program.
* ['KuskoHarvUtils'](https://github.com/bstaton1/KuskoHarvUtils) (`r paste0("v", packageVersion("KuskoHarvUtils"))`): contains several helper functions used throughout the 'KuskoHarv\*' family of packages.

To ensure installation of the exact package versions used upon publication, install these packages as follows:

```{r, eval = FALSE, echo = TRUE}
# FIXME: finalize these REFS
remotes::install_github("bstaton1/KuskoHarvUtils", ref = "INSERT_FINAL_REF")
remotes::install_github("bstaton1/KuskoHarvEst", ref = "INSERT_FINAL_REF")
remotes::install_github("bstaton1/KuskoHarvData", ref = "INSERT_FINAL_REF")
remotes::install_github("bstaton1/KuskoHarvPred", ref = "INSERT_FINAL_REF")
```

### CRAN Packages

The table below shows all R packages (and their versions at time of publication; _typically_ should not matter, included for completeness) that are specifically called (typically with `pkg::fn()`) or loaded (using `library(pkg)`).
Users will need to have these packages installed prior to executing any of the code in this repo.

<details>
<summary><b>Click to Expand/Hide Packages Table</b></summary>

```{r pkg-table}

# detect all packages called specifically
used_pkgs = renv::dependencies(quiet = TRUE)$Package |> 
  unique() |> 
  sort()

# exclude any packages you don't wish to include in the table here
# e.g., anything used solely in building this Rmd
used_pkgs = used_pkgs[!used_pkgs %in% c("renv", "sessioninfo")]

# get the version of each package
versions = sapply(used_pkgs, function(pkg) paste(packageVersion(pkg), collapse = "."))

# get the description (i.e., title field of DESCRIPTION file) of each package
desc = sapply(used_pkgs, function(pkg) paste(packageDescription(pkg)$Title, collapse = ".")) |> 
  stringr::str_replace("\\n", " ")

# build a matrix
tab = cbind(pkg = used_pkgs, version = versions, desc = desc)
rownames(tab) = NULL

# build package name as a markdown link, with a URL placeholder
tab[,"pkg"] = paste0("[`", tab[,"pkg"], "`](URL)")

# function to get the URL that will replace the placeholder
# if it is a KuskoHarv* package, must link to my GitHub
# otherwise, use standardized CRAN link
get_url = function(pkg) {
  
  # determine if this package is one the the family
  is_kusko = stringr::str_detect(pkg, "KuskoHarv")
  
  # use my GitHub if so, CRAN if not
  if (is_kusko) {
    url = paste0("https://www.github.com/bstaton1/", pkg)
  } else {
    url = paste0("https://CRAN.R-project.org/package=", pkg)
  }
  
  # return the output
  return(url)
}

# get the URLs for each package and perform the replacement
tab[,"pkg"] = stringr::str_replace(tab[,"pkg"], "URL", sapply(used_pkgs, get_url))

# return the kable
kableExtra::kbl(tab, "markdown", col.names = c("Package", "Version", "Description"), align = "lrl")
```


</details>

Running the code below will display the packages not already installed on your machine:

```{r, eval = TRUE, echo = FALSE}
check_code = paste0("```R\npkgs <- c(", knitr::combine_words(used_pkgs, before = '"', and = "", sep = ', '), ")\npkgs[!pkgs %in% pkgs]\n```")

# pkgs = c(
#   "DHARMa", "KuskoHarvPred", "KuskoHarvUtils", "lubridate", 
#   "MuMIn", "qgam", "reshape2", "scales", "stringr", "this.path")
# pkgs[!pkgs %in% pkgs]
```

`r check_code`

## Reproducing Article Content

To reproduce all content presented in the manuscript, open [RStudio](https://posit.co/download/rstudio-desktop/) to the `KuskoHarvPred-ms-analysis.Rproj` location and execute:

``` r
fig_type = "pdf"                   # figure file extension; pdf or png
source("make-figures.R")           # exports figure files for manuscript
source("make-tables.R")            # exports .csv files for manuscript
source("make-residual-figures.R")  # exports residual diagnostic plots
```

After executing this code, the there will be two new subdirectories: `figures` and `tables` storing the content used in building the manuscript.

## Session Info

<details>
<summary><b>Click to Expand/Hide Session Info</b></summary>

```{r message = FALSE, warning = FALSE}
junk = suppressPackageStartupMessages({
  sapply(used_pkgs, library, character.only = TRUE)
})
```

```{r}
sessioninfo::session_info()
```

</details>
